# Imports and Setup

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Each chapter includes the following code block, which is used to set the python environment. This should be changed to *your* python path to be run.
```{r python_setup, echo=TRUE}
library(reticulate)
library(knitr)
opts_chunk$set(engine.path='/Users/nathanielstarkman/miniconda3/bin/python3.7')
```

The following imports and definitions may be found in the `src` folder of this project. They are included here for easy perusal, but are imported in each chapter with the following code block (hidden in chapters)

```{python, echo=TRUE, eval=TRUE}
from src import *
```

## Imports

These are the important imports from `src`

```{python example_imports, echo=T, eval=F}
import pickle

import sympy as sp
from sympy import pprint, Symbol, init_printing

init_printing()

from src.parameters import (  # Parameters
    # dummy's
    dummyL, dummyO, dummyMinus, dummyZero, dummyPlus,
    legendre_products_constants,
    # variables
    tau, tau0, mu, l, k, lge2, lge3,
)

from .parameters import (LgP, DeltaT, DeltaP)  # Functions to Make Parameters

```


## Symbols and Sympy Functions  {#symbols}

There are many variables. Here is a table, in alphabetical order.

| Variable      | Symbol               | Explanation                               |
| ------------- |:--------------------:| -----------------------------------------:|
| `tau`         | $\tau$               | conformal time / distance                 |
| `tau0`        | $\tau_0$             | current conformal time                    |
| `mu`          | $\mu$                | angle                                     |
| `l`           | $\ell$               | Legendre $\ell$                           |
| `k`           | $k$                  | vector                                    |
| `dummyL`      | $\ell$               | dummy Legendre $\ell$                     |
| `dummyO`      | $\mathcal{O}$        | dummy Taylor expansion order              |
| `tauc`        | $\tau_C(\tau)$       | inverse of Thompson scatter rate          |
| `kappa`       | $\kappa(\tau)$       | Thompson scattering                       |
| `dkappa`      | $\dot{\kappa}(\tau)$ | Thompson scattering rate                  |
| `a`           | $a(\tau)$            | scale factor                              |
| `R`           | $R(\tau)$            | $\frac{3\rho_b}{4\rho_\gamma}$            |
| `Psi`, `Phi`  | $\Psi$, $\Phi$       | Bardeen potential                         |
| `DT    `      | $\Delta_T$           | temperature fluctuation                   |
| `DP`          | $\Delta_P$           | Polarization fluctuation                  |
| `Sx`          | $S_{TP}(\tau)$       | $\Delta_{T2} + \Delta_{P2} - \Delta_{P0}$ |

<!-- TODO? Do the table programattically from the namespacce -->


### Variable Details

Many of the variables have both order expansions in powers of `tauc` as well as multipole expansions in `l`. Additionally, many variables are implicitly functions of `tau`. In order to make reading these variables easier, they have been implemented using a custom Sympy function class that overloads the base LaTeX functionality. As example, `a` is $a(\tau)$, but will appear as $a$ unless its argument is substituted to another variable ($a(x)$ would appear as is). Similarly, `DT` is $\Delta_{T,\rm{multipole}}^{(\rm{order})}(\tau)$ but shows as $\Delta_T$ unless the order, multipole or argument are changed. When the order or multipole do NOT appear, it means `DT` for ALL orders and/or multipoles.

Besides overloading the LaTeX functionality, some functions, such as `LgP` and `DP` have custom `.doit()` methods and arguments to prevent their being expanded by their definitions (see next section).


### Dummy Variables
Dummy variables are used in function construction as a stand-in for unspecified values. This is done to protect variables from improper substitutions.

Some of the dummy variables used in this paper are:

- Legendre degree $l$:
```{python}
dummyL = Symbol(r"\mathcal{\ell}")  # Legendre l
```

- Taylor expansion order $\mathcal{O}$:
```{python}
dummyO = Symbol(r"\mathcal{O}")  # order
```

- - -

## Relations {#relations}
Sympy has powerful symbolic substutitution capabilities. We store relations and particular solutions in dictionaries for fast access and Sympy compatibilty.

```{python relations}

rels = {
    Sx : DT_a_2 + DP_a_2 - DP_a_0,
    tauc: 1/dkappa
#     R : 
}

sols = {}  # general solutions

sols_0 = {}  # 0th order solution
sols_1 = {}  # 1st order solution

```

- - -
## Passing Variables

Storing variables and relations for later chapters.

```{python, echo=T}
vars = {}

# save variables
vars['rels'] = rels
vars['sols'] = sols
vars['sols_0'] = sols_0
vars['sols_1'] = sols_1

with open('src/pickled/01.pkl', 'wb') as file:
    pickle.dump(vars, file)
```

<!-- You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015]. -->
